---
title: "Creating_Canopy_Height_Models"
author: "Lavran Pagano"
date: "3/16/2021"
output: html_document
---
###import packages
```{r }
library(lidR)
library(stringr)
library(spatialEco)
library(SpaDES)
```
### Read in .las file and use inverse distance weighting to make sure that the minum value is zero
```{r}
las <- readLAS("/Users/lavran_pagano/Desktop/Brauerlas/245267.las")# imput your on path to your .lasfile
lasn <- lasnormalize(las, knnidw(),na.rm = TRUE) #inverse distance weighting
```
### Create a canopy height model.
```{r}
chm <- grid_canopy(lasn, 0.25, pitfree(c(0,2,5,10,15), c(0,1), subcircle = 0.2))# Khosravipouret al. 2014
```
### Our lidar files were using feet as units so we need to convert all values to meters
```{r}
CHM_m <- chm * 0.3048
```
### Making double sure that there are no points above 30 meters or below zero meters
```{r}
CHM_m[CHM_m < 2] <- 0
CHM_m[CHM_m > 30] <- 0
```
### Aply a Gaussian filter to remove spirious points
```{r}
gf <- focalWeight(CHM_m, 2, "Gauss")
CHMrg <- focal(CHM_m, w=gf, na.rm=TRUE)
```
### Write to a raster
```{r}
writeRaster(CHMrg, filename = "Canopy_Height_Model", bylayer = TRUE, format = "GTiff", overwrite = TRUE)
```

